\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
added a decide input to the dependency-set algorithm

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, and the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$), if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}

>>>>

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, and an input interface $\opn{decide}\left( c,\mathcal{D} \right)$ (meant to receive inputs from the agreement sub-algorithm), where $p\in P$ is the process executing the call.
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$), if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
    \item If a suggestion $\opn{suggest}_p(c,\mathcal{D})$ has been made and no input $\opn{decide}_q\left( c,\mathcal{D'} \right)$ is observed, then eventually a new suggestion $\opn{suggest}_r\left( c,\mathcal{D''} \right)$ for $r\neq p$ is made.
\end{enumerate}
